---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Loading

Loading 

```{r}
library(restimoter)
dir_path <- system.file("extdata", package = "restimoter")
obj <- load_restimote_log(dir_path)
obj <- load_restimote_companion_log(dir_path, obj = obj)
```
Data is now loaded in a list object 

we can access restimote log easilly by 
```{r}
head(obj$log)

```

```{r}
head(obj$companion)
```

# Cleaning up

First we need ot add in helper columns
```{r}
obj <- preprocess_companion_log(obj)
obj <- preprocess_restimote_log(obj)
```

Then we may remove wrong or mistaken trials.
In my research notes, I put down that the 7th and 8th trial were registyered in the companion app by mistake. So we remove them
```{r}
obj <- remove_pointing(obj, c(7:8))
```

# Results

# Plotting
requires ggplot 

if we want nice graphs, we need to set the location boundaries first
```{r}
obj$location_size <- c(25, 25)
```

#Smoothing
```{r}
library(forecast)

```

df_estimote$time.diff <- c(0, df_estimote$Time[2:n]-df_estimote$Time[1:n-1])
df_estimote$angle.diff <- c(0, df_estimote$Orientation[2:n]-df_estimote$Orientation[1:n-1])

points <- data.matrix(df_estimote[2:3])
df_estimote$position.diff <- euclid_distance_col(points)

df_estimote$speed <- df_estimote$position.diff/df_estimote$time.diff

plt <- ggplot(df_estimote, aes(Position.X, Position.Y, color = (Time)))
plt + geom_point()

ggplot(df_estimote, aes(Time, speed, color = Accuracy)) + geom_line()


plt <- ggplot(df_estimote, aes(Time, Orientation))
plt + geom_path()

# smoothing - maybe do interactively
df_estimote$smoothed <- 0
smooth <- function(df, level){
  df$smoothed <- level
  df$Position.X <- ma(df$Position.X, level)
  df$Position.Y <- ma(df$Position.Y, level)
  return(df)
}

df_estimote_smoothed_1 <- smooth(df_estimote, 50)

df_estimote_all <- do.call("rbind", list(df_estimote, df_estimote_smoothed_1))

plt <- ggplot(df_estimote_all, aes(Position.X, Position.Y, color = as.factor(smoothed)))
plt + geom_path()

plt <- ggplot(df_estimote_smoothed_1, aes(Position.X, Position.Y))
plt + geom_point()

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
