---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Loading

Loading 

```{r}
library(restimoter)
dir_path <- system.file("extdata", package = "restimoter")
obj <- load_restimote_log(dir_path)
obj <- load_restimote_companion_log(dir_path, obj = obj)
```
Data is now loaded in a list object 

we can access restimote log easilly by 
```{r}
head(obj$log)

```

```{r}
head(obj$companion)
```

# Cleaning up

First we need ot add in helper columns
```{r}
obj <- preprocess_companion_log(obj)
obj <- preprocess_restimote_log(obj)
```

Then we may remove wrong or mistaken trials.
In my research notes, I put down that the 7th and 8th trial were registyered in the companion app by mistake. So we remove them
```{r}
obj <- remove_pointing(obj, c(7:8))
```

# Results

# Plotting
requires ggplot 

if we want nice graphs, we need to set the location boundaries first
```{r}
obj$map_limits <- list(x = c(0, 25), y = c(0, 25))
```

#Smoothing
```{r}
library(forecast)

```

df_estimote$time.diff <- c(0, df_estimote$Time[2:n]-df_estimote$Time[1:n-1])
df_estimote$angle.diff <- c(0, df_estimote$Orientation[2:n]-df_estimote$Orientation[1:n-1])

points <- data.matrix(df_estimote[2:3])
df_estimote$position.diff <- euclid_distance_col(points)

df_estimote$speed <- df_estimote$position.diff/df_estimote$time.diff

plt <- ggplot(df_estimote, aes(Position.X, Position.Y, color = (Time)))
plt + geom_point()

ggplot(df_estimote, aes(Time, speed, color = Accuracy)) + geom_line()

plt <- ggplot(df_estimote, aes(Time, Orientation))
plt + geom_path()

# smoothing - maybe do interactively
df_estimote$smoothed <- 0
smooth <- function(df, level){
  df$smoothed <- level
  df$Position.X <- ma(df$Position.X, level)
  df$Position.Y <- ma(df$Position.Y, level)
  return(df)
}

df_estimote_smoothed_1 <- smooth(df_estimote, 50)

df_estimote_all <- do.call("rbind", list(df_estimote, df_estimote_smoothed_1))

plt <- ggplot(df_estimote_all, aes(Position.X, Position.Y, color = as.factor(smoothed)))
plt + geom_path()

plt <- ggplot(df_estimote_smoothed_1, aes(Position.X, Position.Y))
plt + geom_point()